Online learning methods for financial time series forecasting

### 2017-12-15 slides/defense-slides.tex
Ready to present

>>>>

\section{Volatility models}

\begin{frame}
\frametitle{Volatility models}
For many years the most popular methods for estimating financial volatility were
the autoregressive conditional heteroskedasticity (ARCH) models
and the general ARCH (GARCH) models. For instance, the
GARCH(1,1) defines returns $y_t$ and volatility $\sigma_t$ as:

\begin{eqnarray*}
    y_t &=& \sigma_t \epsilon_t \\
     \sigma_t^2 &=& \alpha_0 + \alpha_1 \epsilon_{t-1}^2 + \beta_1
     \sigma_{t-1}^2
\end{eqnarray*}

\noindent where $\epsilon_t$ is standard Gaussian white noise,
$\alpha_0,\alpha_1,\beta_1 \geq 0$ are required to ensure that the
variance will never be negative and $\alpha_1+\beta_1 <1$ is needed to
guarantee a weakly stationary process.
\end{frame}
